%-------------------------
% Resume in Latex
% Author : Ankit Bhagat
% License : MIT
%-------------------------

\documentclass[a4paper,11pt]{article}
\setlength{\footskip}{4.08003pt}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}

\usepackage{charter}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, topsep=0pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Ankit Bhagat} \\ \vspace{2pt}
    \small
    \href{tel:+919102281008}{\underline{+91 9102281008}} $|$
    \href{mailto:ankitbhagat.dev@gmail.com}{\underline{ankitbhagat.dev@gmail.com}} $|$
    \href{https://linkedin.com/in/your-linkedin}{\underline{LinkedIn}} $|$
    \href{https://github.com/ankitsensei}{\underline{GitHub}} $|$
    \href{https://ankitbhagat-portfolio.vercel.app}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------

\section{Professional Summary}

Full Stack Web Developer specializing in building scalable web applications using React, Node.js, Express.js, and MongoDB. Experienced in developing responsive user interfaces, REST APIs, and deploying production-ready applications. Passionate about modern JavaScript technologies and writing clean, maintainable code.

%-----------EXPERIENCE-----------

\section{Experience}

\begin{itemize}[leftmargin=0.15in,label={}]
\small{

\item{
\textbf{Web Developer (Freelance)} $|$ \emph{React, Tailwind CSS, Supabase} \hfill \emph{2025}\\
ClassyPictures \hfill Hybrid, Chakradharpur

\resumeItemListStart
\resumeItem{Developed a modern photography portfolio website using React.js, Tailwind CSS, and Supabase.}
\resumeItem{Implemented online booking functionality and GSAP animations, reducing manual communication and improving user engagement.}
\resumeItemListEnd
}

\item{
\textbf{Frontend Developer (Contract)} $|$ \emph{React, Tailwind CSS, GSAP} \hfill \emph{2024}\\
Hack United \hfill Remote

\resumeItemListStart
\resumeItem{Built a responsive hackathon website using React.js and Tailwind CSS.}
\resumeItem{Created reusable UI components and smooth animations, improving development speed and page performance.}
\resumeItemListEnd
}

}
\end{itemize}

%-----------PROJECTS-----------

\section{Projects}

\begin{itemize}[leftmargin=0.15in,label={}]
\small{

\item{
\textbf{The North Face} $|$ \emph{React, Node.js, Express, MongoDB, Tailwind CSS}
\hfill
\underline{\href{https://github.com/ankitsensei}{GitHub}}

\resumeItemListStart
\resumeItem{Built a full-stack MERN e-commerce platform featuring JWT authentication, shopping cart, and product management.}
\resumeItem{Integrated Stripe payments, Cash on Delivery, order tracking, and an admin dashboard.}
\resumeItemListEnd
}

\item{
\textbf{Rhythm} $|$ \emph{React, TypeScript, Tailwind CSS}

\resumeItemListStart
\resumeItem{Developed a Spotify-inspired music player using the YouTube Data API.}
\resumeItem{Implemented song search, playback controls, keyboard shortcuts, responsive design, and modern UI.}
\resumeItemListEnd
}

}
\end{itemize}

%-----------SKILLS-----------

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in,label={}]
\small{
\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, C, C++, Rust} \\

\textbf{Frontend}{: React.js, Tailwind CSS, HTML5, CSS3} \\

\textbf{Backend}{: Node.js, Express.js} \\

\textbf{Databases}{: MongoDB, MySQL, Supabase, Firebase} \\

\textbf{Tools}{: Git, GitHub, Postman, Linux}
}
}
\end{itemize}

%-----------EDUCATION-----------

\section{Education}

\begin{itemize}[leftmargin=0.15in,label={}]
\small{

\item{
\textbf{Jharkhand Rai University} \hfill Ranchi, Jharkhand\\
Bachelor of Technology in Computer Science and Engineering
\hfill
\emph{2024 -- 2028}\\
CGPA: 8.5
}

}
\end{itemize}

\end{document}