%-------------------------}
% Resume in Latex
% Author : Jatin
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}
\setlength{\footskip}{4.08003pt}

% \usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
% \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
% \usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
% \usepackage{fancyhdr}
% \usepackage[english]{babel}
% \usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, topsep=0pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jatin} \\\vspace{1pt}\small
    \href{tel:+917765814914}{\underline{+91 7765814914}} $|$
    \href{mailto:heyjatinn@gmail.com}{\underline{heyjatinn@gmail.com}} $|$
    \href{https://linkedin.com/in/jatinnkumar}{\underline{linkedin.com/in/jatinnkumar}} $|$
    \href{https://github.com/jatindotdev}{\underline{github.com/jatindotdev}}
\end{center}

\section{Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            {\textbf{Software Engineer} $|$ \emph{Kotlin, Spring, PostgreSQL, TypeScript} \hfill \emph{May 2026 -- Present}}\\
            {Headout \hfill Bangalore, India}
            \resumeItemListStart
                \resumeItem{Works on Headout's B2B distribution layer, supporting API, Affiliate, and Agent channels that power third-party sales and integrations.}
            \resumeItemListEnd
        }
    }
    \small{
        \item{
            {\textbf{Software Engineer Intern} $|$ \emph{Kotlin, Spring, PostgreSQL, TypeScript} \hfill \emph{May 2025 -- May 2026}}\\
            {Headout \hfill Bangalore, India}
            \resumeItemListStart
                \resumeItem{Built backend systems with \textbf{Salesforce CRM integration} and automated affiliate Terms \& Conditions acceptance through \textbf{Spotdraft} to streamline partner onboarding.}
                \resumeItem{Shipped \textbf{Creator Monetary Campaigns} and \textbf{Opportunities Dashboard} end to end, enabling referral campaign launches, wallet credits, and partner application reviews.}
                \resumeItem{Built \textbf{partner.headout.com/docs} on \textbf{Mintlify} with an API playground, AI assistant, and integration guides; later extended campaign infrastructure to support generic partner campaign URLs for B2B partnerships.}
            \resumeItemListEnd
        }
    }
    \small{
        \item{
            {\textbf{SDE Intern} $|$ \emph{Node.js, TypeScript, React Native, AWS CDK, Serverless} \hfill \emph{April 2024 -- April 2025}}\\
            {Emendo \hfill Remote, US}
            \resumeItemListStart
                \resumeItem{Built a construction-management app in React Native that automated material tracking and ledger updates for contractors.}
                \resumeItem{Developed a real-time receipt and document extraction service to automate downstream processing workflows.}
            \resumeItemListEnd
        }
    }
    \small{
        \item{
            {\textbf{App Development Intern} $|$ \emph{Flutter, Dart, ESP} \hfill \emph{Sep 2023 -- Dec 2023}}\\
            {Climec Labs \hfill Chennai, India}
            \resumeItemListStart
                \resumeItem{Built a cross-platform IoT app for air purifiers, supporting device controls, fan-speed changes, and real-time air-quality monitoring.}
            \resumeItemListEnd
        }
    }
\end{itemize}

\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
             {\textbf{Loop} $|$ \emph{SwiftUI, SwiftData, Spotify iOS SDK} \hfill \underline{\href{https://github.com/jatindotdev/loop}{GitHub}}}
             \resumeItemListStart
                \resumeItem{Built an iOS music app for trimmed Spotify clips with custom start and end points stored in SwiftData.}
                \resumeItem{Implemented auto-advance, now-playing controls, and URI/link import for a smoother playlist-style flow.}
             \resumeItemListEnd
        }
    }
    \small{
        \item{
             {\textbf{KzCMS} $|$ \emph{Node.js, TypeScript, AWS S3} \hfill \underline{\href{https://github.com/srm-kzilla/kzcms}{GitHub}}}
             \resumeItemListStart
                \resumeItem{Co-led CMS development, adding role-based access control and real-time publishing for the club site.}
                \resumeItem{Integrated AWS S3 to support scalable digital asset management and media sharing.}
             \resumeItemListEnd
        }
    }
\end{itemize}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Kotlin, Dart, Python, Go, SQL, C and C++} \\
     \textbf{Frameworks}{: React, Next.js, Flutter, React Native } \\
     \textbf{Development and Cloud}{: Node.js, AWS CDK and AWS SDK (S3, EC2, SQS, SNS, RDS), Docker, Linux Servers, Nginx } \\
     \textbf{Databases}{: MongoDB, PostgreSQL, MySQL, Supabase, Firebase } \\
     \textbf{Developer Tools}{: Git, VS Code, Xcode } }}
 \end{itemize}

\section{Leadership}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {\textbf{Associate Technical Lead} $|$ {SRMKZILLA, GDSC SRM} \hfill \emph{2022 -- 2024}}\\
     {Led technical projects, mentored developers, and helped ship internal tools and club platforms for student developer communities.}
    }}
\end{itemize}

\section{Hackathons and Prizes}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {\textbf{Innerve, AIT, Pune} $-$ \emph{Educative.AI, an EduTech product, placed us in the top five in India at the finals.}}
     \\
     {\textbf{Hacknova, Newton School Coding Club} $-$ \emph{Secured 2nd Position winning a prize pool of Rs. 10,000}}
    }}
 \end{itemize}

\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            {\textbf{SRM Institute of Science and Technology} \hfill \emph{Chennai, Tamil Nadu}}\\
            {B.Tech in Computer Science and Engineering \hfill \emph{Sept 2022 -- May 2026}}
        }
    }
\end{itemize}

\end{document}
